\documentclass{article}
\usepackage{amsmath}
\begin{document}
\begin{flushleft}
	
	\huge {\textbf{\textit{LIBLEARN}}}\\[1.5cm]	
	\small Ashish Varun Reddy \\[0.10cm]
	\textbf{IIT(ISM) Dhanbad}\\[0.55cm]
	\textbf{Description} : This library contains machine learning models like linear regression, polynomial regression, logistic regression, decision trees, K- nearest neighbours classification, N-layer neural network, K-means Clustering.\\[0.50cm]
	\textbf{Features}: \\[0.2cm]
	\begin{itemize}
		\item Importable models: models are created such a way that they can be imported and use wherever we want.
		\item Either it is supervised learning or unsupervised learning model this library contains the required model.
	\end{itemize}
	\textbf{Technology Stack}: \\[0.220cm]
	\begin{enumerate}
		\item python
		\item basic libraries like numpy, pandas and matplotlib
		\item google colaboratory
	\end{enumerate}
\textbf{Brief Implementation details} : I think I want to work on the project from day 1 and simultaneously while learning from the internet about the topic. I will first start with easy ones like linear regression and then polynomial regression. Then I will jump into logistic regression and complete it . After it I will go to N-layered neural networks. After completing it, I will implement decision trees , k-Neighbors classification and unsupervised learning topics like K-means clustering.\\[0.60cm]

\renewcommand{\labelitemi}{}
\textbf{Week Wise timeline}: \\[0.5cm]
\begin{align}
\text{ week1 &: linear and polynomial regression.}\\
\text{week2 &: logistic regression and half of N-layered Neural Network.}\\
\text{week3 &: Other half of N-layered Neural Network and decision trees.}\\
\text{week4 &: K-Neighbours classification and K-means clustering.}\\
\end{align}

\textbf{About Me}: \\[0.35cm]
\renewcommand{\labelitemi}{-}
\begin{itemize}
 \item My name is Ashish Varun Reddy \\
 \item I am studying in first year of Bachelor of Technology in Computer Science and Technology. \\
 \item I want to be selected for this project for improving and showcasing my skills in the field of Artificial intelligence.
\end{itemize}


\end{flushleft}






\end{document}
